---
title: "Report"
author: "Alain Danet"
output: html_document
---

```{r}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE 
)

library(drake)
library(tidyverse)
library(magrittr)
library(cowplot)
#theme_set(theme_cowplot())
```

# Research questions

## State of the art

- Report of community biomass (or number of individual) collapses in many
  ecosystems
- Modification of community are linked to modification in network structure 
- Studies have been interested in how network assembles or disassembles
  themselves.
- However, the lack of availability of such empirical dataset have prevented the
answering to this question.  
  
- Questions:
  1. Are assembly and disassembly of networks symmetric processes ?


# Results

## Temporal dynamics

```{r}
p_cap <- paste0(
  "Temporal dynamics of biomass and temporal dynamics of
  metrics for 10 randomly selected communities."
)
```

```{r p-tmp-dyn, cache = FALSE}
loadd(temporal_dynamics_plot)

p <- vector(mode = "list", length = 10)
for (i in seq_len(length(p))) {
  to_plot <- temporal_dynamics_plot %>% 
    filter(station == sample(temporal_dynamics_plot$station, 1))
  p[[i]] <- cowplot::plot_grid(plotlist = to_plot$plot, labels = to_plot$station)
} 
p
```

## Links betwenn temporal dynamics

```{r b-bivar-cap}
bivar_cap <- paste0(
  "Links between temporal dynamics of biomass and temporal dynamics of
  metrics for the communities which have a median biomass across time inferior
  to the median of the station (little) and the other (big)"
)
```


```{r p-bivar, cache = FALSE, fig.cap = bivar_cap, fig.height = 10}
loadd(net_dyn_lm)
loadd(net_dyn_lm_plot)


cowplot::plot_grid(
  cowplot::plot_grid(plotlist = net_dyn_lm_plot$plot[1:4], ncol = 2),
  cowplot::plot_grid(plotlist = filter(net_dyn_lm_plot, group == "big")$plot[1:4], ncol = 2),
  ncol = 1, 
  axis = "rlbt",
  align = "hv",
  label_y = 1.01,
  label_x = .40,
  labels = c("Little community", "Big community")
)
 
cowplot::plot_grid(
  cowplot::plot_grid(plotlist = net_dyn_lm_plot$plot[5:8], ncol = 2),
  cowplot::plot_grid(plotlist = filter(net_dyn_lm_plot, group == "big")$plot[5:8], ncol = 2),
  ncol = 1, 
  axis = "rlbt",
  align = "hv",
  label_y = 1.01,
  label_x = .40,
  labels = c("Little community", "Big community")
)
```

- Intercept close to 0 for all but richness in big communities 
- Same slope between big and little communities except for connectance 

```{r}
loadd(temporal_dynamics_coef)
loadd(data)
first_year_biomass <-
  data %>%
  filter(nb_year == 0) %>%
  select(station, biomass, rel_bm, log_bm, rel_log_bm) %>%
  pivot_longer(-station, names_to = "coeff", values_to = "first_year") %>%
  group_by(coeff) %>%
  mutate(com_size = ifelse(first_year < median(first_year, na.rm = TRUE), "little", "big"))
median_biomass <- 
  data %>%
  select(station, biomass, log_bm) %>%
  pivot_longer(-station, names_to = "coeff", values_to = "biomass") %>%
  group_by(station, coeff) %>%
  summarise(bm_med = median(biomass, na.rm = TRUE)) %>%
  ungroup()

temporal_dynamics_coef %>%
  filter(term %in% "slope", coeff %in% c("biomass", "log_bm")) %>%
  select(1:4) %>%
  pivot_wider(names_from = "term", values_from = estimate) %>%
  left_join(first_year_biomass, by = c("station", "coeff")) %>%
  ggplot(aes(x = first_year, y = slope)) +
  geom_point(aes(color = com_size)) +
  facet_wrap(~coeff, scales = "free") +
  labs(x = "First year biomass (g)", y = "Slope (g.y^-1)")

loadd(biomass_group)
temporal_dynamics_coef %>%
  filter(term %in% "slope", coeff %in% c("biomass", "log_bm")) %>%
  select(1:4) %>%
  pivot_wider(names_from = "term", values_from = estimate) %>%
  left_join(median_biomass, by = c("station", "coeff")) %>%
  left_join(biomass_group, by = c("station")) %>%
  ggplot(aes(x = bm_med, y = slope)) +
  geom_point(aes(color = com_size)) +
  facet_wrap(~coeff, scales = "free") +
  labs(x = "Median biomass (g)", y = "Slope (g.y^-1)")
```

```{r}
data %>%
  group_by(station) %>%
  summarise(med_bm = median(biomass)) %>%
  ggplot(aes(x = med_bm)) +
  geom_histogram() +
  labs(x = "Median total biomass over time by station (g)")
```

```{r, eval = FALSE}
slope_com_net <- temporal_dynamics_coef %>%
  filter(!coeff %in% get_biomass_var(), term == "slope") %>%
  select(station, coeff, estimate) %>%
  pivot_wider(names_from = "coeff", values_from = estimate)

absolute_slope_biomass <- temporal_dynamics_coef %>%
  filter(coeff %in% get_biomass_var(), term == "slope") %>%
  select(station, coeff, estimate) %>%
  mutate(
    absolute_slope =  abs(estimate),
    trend_sign = if_else(estimate > 0, "positive", "negative")
  ) %>%
  left_join(slope_com_net, by = "station") 

metrics <- unique(temporal_dynamics_coef$coeff)[!unique(temporal_dynamics_coef$coeff) %in% get_biomass_var()]

p <- vector("list", length = length(metrics))
for (i in seq_along(metrics)) {
  p[[i]] <- 
    absolute_slope_biomass %>%
    ggplot(aes_string(x = "absolute_slope", y = metrics[i])) +
    geom_point(aes(color = trend_sign)) +
    facet_wrap(facets = ~ coeff, scales = "free") +
    labs(title = metrics[i])
}
p
```

# Methods
