---
title: Appendix
subtitle:
author: Alain Danet, Maud Mouchet, Loubna El Madouri, Elisa Thébault and Colin Fontaine (ordre non fixé)
date: \today 
output:
  bookdown::pdf_document2:
    fig_caption: true 
    keep_tex: true
    toc: true
fontsize: 12pt
header-includes:
   - \usepackage{natbib}
   - \newcommand{\beginsupplement}{\renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}} 
   - \usepackage{float}
   - \usepackage[table]{xcolor}
   - \usepackage{multirow}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
number_sections: true
---

```{r}
knitr::opts_chunk$set(
  cache = TRUE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.align = "center",
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE
)
```


```{r, echo = FALSE, message = FALSE, collapse = FALSE}

library(drake)
library(tidyverse)
library(magrittr)
library(ggeffects)
library(cowplot)
library(kableExtra)
library(sf)
library(nlme)

mypath <- rprojroot::find_package_root_file
source(mypath("R/variable_shortcut.R")) # Define your custom code as a bunch of
#functions.

source(mypath("R/misc.R"))
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

mytheme <- theme_cowplot() +
background_grid()

theme_set(mytheme)
options(knitr.table.format = "latex")
```
```{r}
var_analysis <- c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "log_bm_std",
  "piel_bm", "piel_nind")
```

\beginsupplement

# Data exploration 


## Maps 

```{r}
loadd(p_st_mono_trends_stable_rich_bm, st_mono_trends_stable_rich_bm)

st_cap <- paste0(
  "Repartion of the", length(st_mono_trends_stable_rich_bm), " stations used in
  the data analysis.")

```

```{r st, fig.cap = st_cap}
p_st_mono_trends_stable_rich_bm
```


## Range of variation 

```{r}
range_cap <- paste0(
  "Range of variation of variables in spatial (vertical line) and temporal
  dataset for the (A) minimum and maximum values and (B) the range (i.e. maximum
    - minimum)."
)
```


```{r range, fig.cap=range_cap, fig.height=10}
loadd(p_range)


plot_grid(plotlist = p_range, nrow = 2, labels = "AUTO")
```


## Correlation


```{r}
cor_cap <- paste0("Correlation plot among variables for spatial and temporal
  relationships. ", "Median values over temporal series in each station were
  used for spatial relationships. ", "For temporal relationships, we used the
  temporal trends in each station. Futhermore, each station was weighted by the
  average error standard on the temporal trends of the variables.")
```


```{r cor, fig.cap=cor_cap}
oldpar <- par()
loadd(corr_plot_med, corr_plot_tps)

set_names_corr <- function(mat = NULL) {
  colnames(mat) <- str_replace_all(colnames(mat), var_replacement())
  rownames(mat) <- str_replace_all(rownames(mat), var_replacement())
  return(mat)
}

corr_plot_tps %<>% set_names_corr(.)
corr_plot_med %<>% set_names_corr(.)

par(mfrow = c(1, 2))
corrplot::corrplot(corr_plot_med, type = "upper", diag = FALSE, order =
  "alphabet")
title("Spatial")
corrplot::corrplot(corr_plot_tps, type = "upper", diag = FALSE, order =
  "alphabet")
title("Temporal trends")
```

\newpage

# Statistical analysis

## Spatial model

```{r}
loadd(est_sp_models, colin_sp_models, sp_models)
```

```{r}
tmp <- map(colin_sp_models, enframe)
t_colin_sp_models <- tibble(vif = tmp, mod = names(colin_sp_models)) %>%
  unnest(vif) %>%
  filter(name %in% c("log_rich_std", "log_bm_std", "ct_ff"), mod == "log_rich_std") %>% #same model for
  #all, so the vif is the same
  rename(Response = name, vif = value) %>%
  select(-mod) %>%
  mutate(vif = map(vif, enframe)) %>%
  unnest(vif) %>%
  mutate(
    value = round(value, 3),
    name = str_replace_all(name, var_replacement()),
    Response = str_replace_all(
      Response,
      c("log_rich_std" = "Richness model", "log_bm_std" = "Biomass model",
	"ct_ff" = "Food-web structure"))
    ) %>%
  spread(name, value)


# colinearity table
kable(t_colin_sp_models,
  row.names = FALSE,
  booktabs = T,
  caption = "Variance Inflation Factor for the linear models in the spatial
  models. NA values indicate that the term in column was not included in the
  modeling of the response variable in row.",
  label = "vif-sp",
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped"))
```

## Temporal model with richness and biomass  

```{r}
loadd(
  resume_bm_rich_mod_mono_trends,
  model_bm_rich_no_covar_no_inc_mono_trends,
  reg_table_bm_rich_mono_trends,
  reg_table_bm_rich_mono_stable_trends,
  reg_table_bm_rich_trends,
  reg_table_bm_rich,
  anova_table_bm_rich_mono_trends,
  anova_table_bm_rich_mono_stable_trends,
  anova_table_bm_rich_trends,
  anova_table_bm_rich,
  anova_bm_rich_mod
)
loadd(st_trends_rich_bm, st_mono_trends_rich_bm,
  st_mono_trends_stable_rich_bm)

loadd(pred_bm_rich_mono_trends, pred_bm_rich, pred_bm_rich_trends,
  pred_bm_rich_mono_stable_trends)
```

We modeled the temporal trends of food-web structure as dependant of the
temporal trends of both species richness and community biomass as: 

$dN = dB + dR + \epsilon$

\newpage

### Only mono trends

We kept only the stations that had monotonic trends for biomass and species
richness, with resulting `r length(st_mono_trends_rich_bm)` stations.

```{r}

plot_grid(plotlist = pred_bm_rich_mono_trends$pred_plot)
```


```{r}
reg_table_bm_rich_mono_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of the network structure and the one of
      community biomass and species richness."
    ),
  label = "reg-rich-mono"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
anova_table_bm_rich_mono_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"ANOVA results for the links between the temporal trends of the network
	structure and the one of community biomass and species richness."
	),
      label = "aov-rich-mono"
      ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

\newpage

### All trends (non monotonic) 

We kept all stations that had a significant trend (decrease or increase) for both
species richness and community biomass, with resulting 
`r length(st_trends_rich_bm)` stations. 

```{r}
plot_grid(plotlist = pred_bm_rich_trends$pred_plot)
```


```{r}
reg_table_bm_rich_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"Regression coefficients for the linear models explaining the links
	between the temporal trends of the network structure and the one of
	community biomass and species richness."
    ),
  label = "reg-rich-trends"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
anova_table_bm_rich_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"ANOVA results for the links between the temporal trends of species
	richness and the temporal trends of the network structure."
	),
      label = "aov-rich-trends"
      ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

\newpage

### All monotonic stations (i.e + monotonic stable)

```{r}
plot_grid(plotlist = pred_bm_rich_mono_stable_trends$pred_plot)
```


```{r}
reg_table_bm_rich_mono_stable_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"Regression coefficients for the linear models explaining the links
	between the temporal trends of the network structure and the one of
	community biomass and species richness."
    ),
  label = "reg-rich-trends"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
anova_table_bm_rich_mono_stable_trends %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"ANOVA results for the links between the temporal trends of species
	richness and the temporal trends of the network structure."
	),
      label = "aov-rich-trends"
      ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```


\newpage

### All stations

We kept all the stations. 

```{r}
plot_grid(plotlist = pred_bm_rich$pred_plot)
```


```{r}
reg_table_bm_rich %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
    caption =
      paste0(
	"Regression coefficients for the linear models explaining the links
	between the temporal trends of the network structure and the one of
	community biomass and species richness."
    ),
  label = "reg-rich-all"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
anova_table_bm_rich %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
  caption =
    paste0(
      "ANOVA results for the links between the temporal trends of species
      richness and the temporal trends of the network structure."
      ),
    label = "aov-rich-all"
    ) %>%
kable_styling(latex_options =c("scale_down", "stripped")) %>%
collapse_rows(columns = 1, valign = "top")
```

## Interaction between community biomass trends and species richness trends

```{r}
loadd(model_bm_rich_int_mono_stable_trends)
```

### ANOVA

```{r}
model_bm_rich_int_mono_stable_trends %>%
  .[names(.) %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")] %>%
  map(., car::Anova) %>%
  map(., tidy) %>%
  map2_dfr(., names(.), ~.x %>% mutate(response = .y) %>% select(response,
      everything())) %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
  caption =
    paste0(
      "ANOVA results with interactions."
      ),
    label = "aov-int"
    ) %>%
kable_styling(latex_options =c("scale_down", "stripped")) %>%
collapse_rows(columns = 1, valign = "top")
#map(model_bm_rich_int_mono_stable_trends, ~try(car::vif(.x)))
```

```{r}
model_bm_rich_int_mono_stable_trends %>%
  .[names(.) %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")] %>%
  map(., tidy) %>%
  map2_dfr(., names(.), ~.x %>% mutate(response = .y) %>% select(response,
      everything())) %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
  caption =
    paste0(
      "Regression results with interactions."
      ),
    label = "aov-int"
    ) %>%
kable_styling(latex_options =c("scale_down", "stripped")) %>%
collapse_rows(columns = 1, valign = "top")
```

### Plots

```{r}
pred_int_rich <- map(model_bm_rich_int_mono_stable_trends,
      ~ggpredict(.x,
        terms = c("log_rich_std", "log_bm_std [quart2]")) %>%
        as_tibble() %>%
        mutate(group = as.numeric(as.character(group))) %>%
        rename("log_rich_std" = x, "log_bm_std" = group)
        ) %>%
enframe(name = "response", value = "pred_int")

ti <- pred_bm_rich_mono_stable_trends %>%
  filter(term == "log_rich_std", response %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")) %>%
  select(response, raw_plot) %>%
  left_join(pred_int_rich) %>%
  mutate(pred_plot_color = pmap(
      list(raw_plot, response, pred_int),
      function(p, resp, pred) {
        p +
          geom_line(data = pred,
            aes(
              y = predicted,
              x = log_rich_std,
              color = as.factor(log_bm_std)
            ), size = 1
          ) +
        scale_color_discrete()
      }
      )
  )
rich_leg <- get_legend(ti$pred_plot_color[[1]])

plot_grid(plotlist = map(ti$pred_plot_color, ~.x + theme(legend.position = "none")), rich_leg)
```

```{r}
test <- pred_int_rich[3, ]$pred_int[[1]] %>%
  select(predicted, log_rich_std, log_bm_std) %>%
  arrange(log_rich_std, log_bm_std)

mat <- reshape2::acast(test, log_rich_std~log_bm_std, value.var = "predicted")
library(plotly)
plot_ly(
  x = ~as.numeric(colnames(mat)),
  y = ~as.numeric(rownames(mat)),
  z = ~mat) %>%
  add_surface()
```


```{r}
pred_int_bm <- map(model_bm_rich_int_mono_stable_trends,
      ~ggpredict(.x,
        terms = c("log_bm_std", "log_rich_std [quart2]")) %>%
        as_tibble() %>%
        mutate(group = as.numeric(as.character(group))) %>%
        rename("log_bm_std" = x, "log_rich_std" = group)
        ) %>%
enframe(name = "response", value = "pred_int")

ti_bm <- pred_bm_rich_mono_stable_trends %>%
  filter(term == "log_bm_std", response %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")) %>%
  select(response, raw_plot) %>%
  left_join(pred_int_bm) %>%
  mutate(pred_plot_color = pmap(
      list(raw_plot, response, pred_int),
      function(p, resp, pred) {
        p +
          geom_line(data = pred,
            aes(
              y = predicted,
              x = log_bm_std,
              color = as.factor(log_rich_std)
            ), size = 1
          ) +
        scale_color_discrete()
      }
      )
  )

bm_leg <- get_legend(ti_bm$pred_plot_color[[1]])
plot_grid(plotlist = map(ti_bm$pred_plot_color, ~.x + theme(legend.position = "none")), bm_leg)
```

```{r, eval=FALSE}
test <- model_bm_rich_int_mono_stable_trends[["ct_ff"]]
co <- coef(test)
pred <- ggpredict(
  test,
  terms = c("log_bm_std ", "log_rich_std")
  ) %>%
  as_tibble() %>%
  mutate(group = as.numeric(as.character(group))) %>%
  rename("log_bm_std" = x, "log_rich_std" = group)

pred$y <- co[1] +
  co["log_rich_std"] * pred[["log_rich_std"]] +
  co["log_bm_std"] * pred[["log_bm_std"]] +
  co["log_rich_std:log_bm_std"] * pred[["log_rich_std"]] * pred[["log_bm_std"]]

# all.equal(pred$y, pred$predicted)

mat <- reshape2::acast(pred, log_rich_std~log_bm_std, value.var = "y")
library(plotly)
plot_ly(
  x = ~as.numeric(colnames(mat)),
  y = ~as.numeric(rownames(mat)),
  z = ~mat, ) %>%
  add_surface() %>%
  layout(scene = list(
      xaxis = list(title = "species richness"),
      yaxis = list(title = "Community biomass"),
      zaxis = list(title = "Connectance")
      ))
```

```{r, eval=FALSE}
mod4_3d <- model_bm_rich_int_mono_stable_trends[
  names(model_bm_rich_int_mono_stable_trends) %in%
    c("ct_ff", "w_trph_lvl_avg")]

pred_list <- map(mod4_3d,
  function (modl, p) {
    co <- coef(modl)
    p$y <- co[1] +
#      co["log_rich_std"] * p[["log_rich_std"]] +
      co["log_bm_std"] * p[["log_bm_std"]] +
      co["log_rich_std:log_bm_std"] * p[["log_rich_std"]] * p[["log_bm_std"]]
    return(p)

  }, p = pred)
```

```{r,eval=FALSE}
mat <- reshape2::acast(
  pred_list$w_trph_lvl_avg,
  log_rich_std~log_bm_std,
  value.var = "y")
plot_ly(
  x = ~as.numeric(colnames(mat)),
  y = ~as.numeric(rownames(mat)),
  z = ~mat, ) %>%
  add_surface() %>%
  layout(scene = list(
      xaxis = list(title = "Community biomass"),
      yaxis = list(title = "species richness"),
      zaxis = list(title = "Avg trophic level")
      ))
```

```{r,eval=FALSE}
test <- model_bm_rich_int_mono_stable_trends[["piel_bm"]]
car::Anova(test)
co <- coef(test)
pred <- ggpredict(
  test,
  terms = c("log_bm_std ", "log_rich_std")
  ) %>%
  as_tibble() %>%
  mutate(group = as.numeric(as.character(group))) %>%
  rename("log_bm_std" = x, "log_rich_std" = group)

pred$y <- co[1] +
  co["log_rich_std"] * pred[["log_rich_std"]] +
  co["log_bm_std"] * pred[["log_bm_std"]] +
  co["log_rich_std:log_bm_std"] * pred[["log_rich_std"]] * pred[["log_bm_std"]]

# all.equal(pred$y, pred$predicted)

mat <- reshape2::acast(pred, log_rich_std~log_bm_std, value.var = "y")
plot_ly(
  x = ~as.numeric(colnames(mat)),
  y = ~as.numeric(rownames(mat)),
  z = ~mat, ) %>%
  add_surface() %>%
  layout(scene = list(
      xaxis = list(title = "species richness"),
      yaxis = list(title = "Community biomass"),
      zaxis = list(title = "Eveness of biomass")
      ))
```



