---
title: "More than space for time: revealing the tight links constraining the temporal dynamics of network structure"
author: "Alain Danet, Maud Mouchet, Loubna El Madouri, Colin Fontaine (ordre non fixé)"
self_contained: yes
date: "`r Sys.Date()`"
tables: yes
bibliography: references.bib 
fontsize: 12pt
output:
  bookdown::html_document2:
    fig_caption: true
    theme: "journal"
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE 
)
```


```{r, results = FALSE}
library(drake)
library(tidyverse)
library(magrittr)
library(cowplot)
library(viridis)
library(kableExtra)
library(sf)
mypath <- rprojroot::find_package_root_file 
source(mypath("R/variable_shortcut.R")) # Define your custom code as a bunch of functions.
source(mypath("R/misc.R"))
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

mytheme <- theme_cowplot() +
background_grid()

theme_set(mytheme)
bookdown::html_document2
library(bookdown)
```
```{r}
net_var_bm <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
      "piel_nind")
net_var_rich <- c("log_bm_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
      "piel_nind")
```


# Methods

## Data selection

We selected the stations that have been monitored at least 10 times on the
1995-2018 period.   

## Food-web inference 

Because we had few informations about trophic interactions between resources, we
selected only the fish-fish interactions in subsequent analysis.

## Food-web and community structure

We characterized food-webs by its connectance, describing the degree of
generalism in a network [@dunne_network_2006, @delmas_analysing_2019]. It is
computed as the ratio between the actual number of links and the number of
potential links ($C = \frac{L}{S(S-1)}$, with $L$ being the number of links and
$S$ the number of trophic species). We also computed the average trophic level,
weighted by the biomass of the trophic species. The trophic level of a trophic
species is computed recursively as 1 added to the mean trophic level of the
preys that it consumes.

We described community structure by its community biomass, species richness and the
evenness of the number of individual and the amount of biomass across species. The evenness was
quantified with the Pielou index, computed as the Shannon diversity index
divided by the number of species ($P = \frac{H'}{N}$, with $H'$ being the
Shannon diversity index and $N$ the number of species).

```{r}
loadd(com_analysis_data, full_data2)
```
```{r}
nb_st <- unique(full_data2$station) %>% length
```


## Classification of temporal trajectories

With the goal to characterize the links among the temporal variations of network
and community structure and the temporal variations of community biomass and
species richness, we characterized the temporal trajectories of network and
community structure at each site. We used a method based on second order
polynomial which allows to assess both the direction and the monotony of
temporal trends [@rigal_method_2020]. To avoid complex variations of biomass and
species richness, we selected the stations that displayed monotonic trends for
theses variable. Over the `r nb_st` stations, the selection procedure resulted
in XX stations for biomass and species richness analysis.

## Spatial  

We selected the same stations that was used for the temporal analysis. 
 
# Statistical analysis

## Temporal trends 

With the aim to test (1) the relationship among the temporal dynamics of network
structure from one side and species richness and community biomass from another
side, (2) if those relationships were different if the communities were
assembling or disassembling, (3) if those relationships were different if
small/big communities, we modelled the dynamics the temporal trends of food-web
structure ($dN$) in function of the temporal trends of community biomass ($dB$) and species
richness ($dR$), if the latter was positive of not (Inc) and with respectively the median
community biomass ($B_i$) and species richness ($R_i$)of the three first years of the temporal
series .

$dN = dB + B_i + dB \times B + Inc \times B_i + dB \times Inc \times B_i$

$dN = dR + R_i + dR \times R_i + Inc \times R_i + dR \times Inc \times R_i$

With:

  - $dN$: temporal trend of network structure and communities structure
  - $dB$: temporal trend of community (log) biomass
  - $dR$: temporal trend of (log) species richness 
  - $B_i$: median community biomass of the first three year
  - $R_i$: median species richness of the first three year
  - $Inc$: Is $dB > 0$?

## Spatial trends

Spatial gradient of food-web structure are partly driven by environmental gradients, so
we controlled relationships among community structure variables by two PCA axis
synthesizing respectively (1) stream size and (2) average temperature and
enrichment. Enrichment was characterized by the average Biological Oxygen
Demand [BOD, @mallin_factors_2006].
 

$N =  B + R + E_1 + E_2 $

With:

  - $N$: median network structure and communities structure
  - $B$: median community biomass
  - $R$: median species richness 


# Results

```{r}
loadd(rsq_sp_mod, summary_table, sp_models, model_summary)
rsq <- summary_table %>%
  filter(y %in% unique(c(net_var_bm, net_var_rich))) %>%
select(y, x, mod_summary_table) %>%
unnest(mod_summary_table) %>%
select(y, x, r.squared, adj.r.squared)
```

```{r}
rsq_nind_bm <- rsq[rsq$y == "piel_nind" & rsq$x == "log_bm_std",]$adj.r.squared %>%
  round(., 3)
rsq_bm_rich <- rsq[rsq$y == "log_bm_std" & rsq$x == "log_rich_std",]$adj.r.squared %>%
  round(., 3)
rsq_tlvl_rich_sp <- rsq_sp_mod$log_rich_std[
  rsq_sp_mod$log_rich_std$Response == "w_trph_lvl_avg", 
  ]$Conditional %>%
    round(., 3)
rsq_piel_bm_rich_sp <- rsq_sp_mod$log_bm_std[
  rsq_sp_mod$log_rich_std$Response == "piel_bm", 
  ]$Conditional %>%
    round(., 3)
```

Overall, we found high heterogeneity in the explicative power of statistical
models linking temporal dynamics of food-web structure and the one of community
biomass and species richness spanning from $R_{adj}^2= `r rsq_nind_bm`$ for the
relationships between to $R_{adj}^2= `r rsq_bm_rich`$ between biomass and
species richness (Table \@ref(tab:rsq)). The spatial relationships among
food-web structure aspects were more performant, with $R_{cond}^2$ varing from 
`r rsq_tlvl_rich_sp` to `r rsq_piel_bm_rich_sp` (Table \@ref(tab:rsq-sp)).

Overall, we found no significant effect of the temporal gain or losses of
communinity biomass biomass and species richness on the relationship between the
temporal trends of community structure and that of biomass and species richness
(Table \@ref(tab:aov-bm), \@ref(tab:aov-rich)).

## Relationships between temporal trends 

### Community structure and community biomass

```{r}
loadd(model_log_bm_f3y_table_medium, model_log_rich_f3y_table_medium)
reg_bm <- model_log_bm_f3y_table_medium$reg_table
#reg_bm[reg_bm$y == ]
```
We found a significant positive relationship between the temporal trends of
community biomass from one side and species richness, average trophic level,
connectance from the other side (Fig. \@ref(fig:bm), Table \@ref(tab:aov-bm)),
meaning that they temporally increased when the community biomass temporally increased and
respectively that they temporally decreased when the community biomass decreased in
time.

We found a significant negative relationship between the temporal trends of
community biomass and that of the pielou of biomass (Figure \@ref(fig:bm), Table
\@ref(tab:aov-bm)), meaning that the eveness of biomass across species
temporally increased when the community biomass temporally decreased and
respectively that the evenness temporally decreased when the community biomass
temporally increased (Fig. \@ref(fig:bm), Table \@ref(tab:aov-bm)). However, we
found no significant relationship between the temporal trends of community biomass and that
of the pielou of individual.

Overall, we did not find effect of assembly/disassembly on the relationships
between the temporal trends of community structure and the one of community
biomass. We also found that the median community biomass had no effect on the
relationship between the temporal trends of community structure and the one of community
biomass.

### Community structure and species richness 

The temporal trends of community biomass, average trophic level, pielou of biomass,
pielou of individual had a positive relationship with that of species richness
(Fig. \@ref(fig:rich), Table \@ref(tab:aov-rich)). However, the direct
relationship between the temporal trends of average trophic level and the one of
species richness was not significant after controling for community biomass temporal
trends [**TO CHECK: refaire tous les modèles temporels en mettant à la fois la
pente des biomasses et de la richness en même temps??**].

We also found that the relationship between the temporal trends of pielou of
individual and connectance and that of species richness was dependant of the
overall species richness of the community (Fig. \@ref(fig:rich), Table
\@ref(tab:aov-rich)), meaning that the relationship between temporal trends of
pielou of individual and that of species richness was more positive as the
community contained more species (Fig. \@ref(fig:rich), Table
\@ref(tab:reg-rich)). While the relationship between temporal trends of pielou
of individual and that of species richness was more negative as the community
contained more species (Fig. \@ref(fig:rich), Table \@ref(tab:reg-rich)).

## Spatial relationships 

### Community structure and community biomass

We found that species richness, connectance, average trophic level were
spatially positively related to community biomass while the pielou of biomass was negatively related to
community biomass (Fig. \@ref(fig:bm), Table \@ref(tab:aov-rich-sp)). However,
we found no spatial relation between the pielou of individual and community
biomass. 

### Community structure and species richness 

We found that community biomass, the pielou of biomass and individual were
positively related to species richness while average trophic level and
connectance were negatively related to
community biomass (Fig. \@ref(fig:rich), Table \@ref(tab:aov-rich-sp)).

# Discussion

- Main results:
  - different mechanisms for richness and biomass
  - space for time subtitution works for biomass and tlvl but not for
    connectance

## Biomass temporal dynamics is linked to the top trophic level

We found that the temporal increase of the average trophic level was positively
linked to increase of community biomass. Increase of average trophic level can
be associated to either gain of biomass in the highest trophic level nor losses
of biomass in the lowest trophic. In our case, such gain or losses of average
trophic level is probably associated to the variations of the presence of large
fishes. This interpretation is confirmed by the finding that the evenness of
biomass, measured by the pielou, decreased through time as community biomass
decrease and reversely, meaning that biomass distribution across species
respectively become respectively less and more even when community biomass
decrease and increase. We also found no relationship between the temporal trends of evenness based
on indivual number and that community biomass, confirming that the temporal trends
of community biomass in our study is linked to few big individuals. It further
indicates that temporal loss of community biomass are linked with the loss of
the higher trophic level. 

We also found in space that evenness of biomass was positively related to
community while eveness of individual number had no relation. It constrasts with
previous studies which found a negative relationship between biomass and eveness
of individual in marine and plant communities [@drobner_relation_1998;
@maureaud_biodiversityecosystem_2019] or studies that found more even plant
communities in terms of individual number display higher community biomass
[@wisley_biodiversity_2000].

We further found that the temporal trends of connectance was positively
linked to that one of community biomass, meaning that connectance increases through
time in a given site when community biomass increases through time and reversely.
This is in line with the fact that the fishes located at higher trophic level
also display a larger number of links as the size of the predation window
increases with the size of the fishes. This result is also in accordance with  
theoretical work showing that higher food-web connectance result in higher
community biomass [@thebaut_food-web_2003].

##  Biomass and richness variation are not the same process 

To the difference with community biomass, the temporal trends evenness of
biomass and individual were positively related to the temporal trends of species
richness, meaning that as community biomass temporally increase, the
distribution of biomass and abondance become more even. Our results indicate
that biomass trends are linked to few big individuals while richness trends are
linked to overall shift in dominance in communities.

Surprinsingly, we found the temporal trends of connectance was not related to
the one of species richness as found spatially in most empirical foodweb
[@dunne_network_2006]. However, the relationship become slightly negative for
species poor communities. An explanation might be that species-rich communities
already contains a significant number of piscivores, which have the most links
whereas species poor communites contains few piscivores.

## Temporal dynamics confirms space for time substitution BEF

Spatially and temporally, the species richness was positively linked to that of
biomass. Spatially, this result is in accordance with numerous studies was
already found in streams [@woods_testing_2020; @danet_species_nodate] but also
in grasslands, salt marches and forests [@hector_plant_1999;
@tilman_biodiversity_2014; @wu_relationship_2015; @li_relationship_2018; but see
@grace_integrative_2016]. Therefore, our results confirm that BEF prediction
works also in time. The positive relationship of species richness on total
biomass might be due to resource use complementarity [@carey_determining_2011],
which is held by niche differentiation [@loreau_biodiversity_1998;
@loreau_partitioning_2001] or to the higher probability of getting high biomass
species with higher species richness [@loreau_biodiversity_2001].

HERE
 @soininen_relationship_2012;

The temporal trend of the average trophic level had no relationship with the
one of species richness. It is surprising because one can imagine that loss and
gain of species would reveal assembly/disassembly mechanisms in terms of trophic
structure. However, we found that when species richness increases, the
distribution of biomass and individuals among species become more even in the
community, meaning that dominance decrease. Species richness has often been
found to be positively or negatively related to individual eveness
[ @maureaud_biodiversityecosystem_2019].

 

## Space for time substitution does not always hold 

We found that community biomass was linked positively related to species richness
both in space and in time, indicating that space for time might be use. In the
same way, we found a positive positive relationship between average trophic
level and community biomass both in time and in space. However, it was not the case
for connectance and average trophic level that were respectively weakly or not
linked to species richness in time whereas our result shows a strong negative
relation in space. Moreover, connectance displayed a strong positive
relationship (move to results?) with biomass in time but not in space. 

Space for time substitution is a widely
used tool in ecology [@pickett_space-for-time_1989; @blois_space_2013;
@damgaard_critique_2019]. However, the drivers of spatial variation might not
be the ones that drive community variation in time. The successional processes
driving the assembly or the disassembly of communities might not be reflected in
spatial gradient.

This result has profound implications for conservation. As more and more
studies report community biomass and richness trends [@hallmann_more_2017;
@ceballos_biological_2017], it is important to note that they might not be
equivalent in terms of consequences on the structure of the community. Further
studies should investigate the temporal trends of several dimensions of
community structure simultaneously because it drives many aspects of ecosystem functioning. 

## Biomass and richness gains and losses are symmetric processes in terms of community structure

We found no case in which gain or losses of biomass and richness lead to
different relationship between the temporal dynamic of community structure and
the one of biomass and species richness. We could have imagine that
extinction/colonisation processes or immigration/extinction debt could have lead
to different relationships.

## Conclusion

We showed that BEF works in time but that richness and biomass temporal trends through
time relates on different ecological processes inside communities. We further
found that space for time subtitution does not always work. 


# References  {-}

<div id="refs"></div>

# Figures {-}

```{r}
fig_bm_cap <- paste0(
  "Relationship between community structure and community biomass. Left panel
  displays the relationships between the temporal trends of community structure
  and the one of community biomass. Lines correspond to the predictions of the
  linear models while the points are colored according the median community
  biomass of the three first years of the given temporal series. The lines surrounding each point represent
  the standard error associated to the temporal trends. Right panel displays the
  spatial relationship between median community structure over time and the
  median community biomass over time."

)

fig_rich_cap <- paste0(
  "Relationship between community structure and species richness. Left panel
  displays the relationships between the temporal trends of community structure
  and the one of species richness. Lines correspond to the predictions of the
  linear models while the points are colored according the median species
  richness of the three first years of the given temporal series. The lines
  surrounding each point represent the standard error associated to the temporal
  trends. Right panel displays the spatial relationship between median community
  structure over time and the median species richness over time."

)
```


```{r}
loadd(p_fig1_2, sp_relation_plot2, predict_plot2)
theme_set(theme_cowplot())
p_bm <- get_plot_fig1_2(predict_plot = predict_plot2, get_list = TRUE,
  bm_x = "log_bm_std", rich_x = "log_rich_std",
  bm_y = c("ct_ff", "w_trph_lvl_avg", "piel_nind", "piel_bm", "log_rich_std") 
  )$bm
names(p_bm) <- c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "piel_nind",
  "piel_bm") 
#plot_grid(plotlist = p_bm)

sp_bm <- sp_relation_plot2 %>%
  filter(x == "log_bm_std")
p_sp_bm <- sp_bm$gg 
names(p_sp_bm) <- sp_bm$y 

reorder_p_sp_bm <- p_sp_bm
reorder_p_sp_bm[[1]] <- p_sp_bm$ct_ff 
reorder_p_sp_bm[[2]] <- p_sp_bm$w_trph_lvl_avg 
reorder_p_sp_bm[[3]] <- p_sp_bm$piel_nind 
reorder_p_sp_bm[[4]] <- p_sp_bm$piel_bm 
reorder_p_sp_bm[[5]] <- p_sp_bm$log_rich_std 
```

```{r}
ti <- list()
for (i in c("log_rich_std", "w_trph_lvl_avg",  "piel_bm", "piel_nind", "ct_ff")) {
  ti[[i]] <- list(p_bm[[i]], p_sp_bm[[i]]) 
}
```



```{r bm, fig.height = 12, fig.cap=fig_bm_cap}
# Make the label on two lines 
top <- plot_grid(plotlist = c(ti[[1]], ti[[2]], ti[[3]], ti[[4]], ti[[5]]), ncol = 2)
fig1 <- plot_grid(top, p_bm[[6]], ncol = 1, rel_heights = c(1, .1)) 
fig1
```

```{r}
p_rich <- get_plot_fig1_2(
  predict_plot = predict_plot2,
  get_list = TRUE,
  rich_x = "log_rich_std",
  rich_y = c("ct_ff", "w_trph_lvl_avg", "piel_nind", "piel_bm", "log_bm_std") 
  )$rich
names(p_rich) <- c(
  "ct_ff", "w_trph_lvl_avg", "piel_nind",
  "piel_bm", "log_bm_std")
#plot_grid(plotlist = p_rich)

sp_rich <- sp_relation_plot2 %>%
  filter(x == "log_rich_std")
p_sp_rich <- sp_rich$gg
names(p_sp_rich) <- sp_rich$y
```

```{r}
fig2_left <- plot_grid(plotlist = p_rich, ncol = 1)
fig2_right <- plot_grid(plotlist = p_sp_rich, ncol = 1)
#plot_grid(plotlist = list(p_bm[[1]], p_sp_bm[[1]], ), ncol = 1)

trich <- list()
for (i in c("log_bm_std", "w_trph_lvl_avg",  "piel_bm", "piel_nind", "ct_ff")) {
  trich[[i]] <- list(p_rich[[i]], p_sp_rich[[i]]) 
}
```

```{r rich, fig.height = 12, fig.cap=fig_rich_cap}
# Make the label on two lines 
top_rich <- plot_grid(plotlist = c(trich[[1]], trich[[2]], trich[[3]], trich[[4]], trich[[5]]), ncol = 2)
fig2 <- plot_grid(top_rich, p_rich[[6]], ncol = 1, rel_heights = c(1, .1))
fig2
```

# Tables {-}

## Statistical models 

### Temporal

```{r}
loadd(model_log_bm_f3y_table_medium, model_log_rich_f3y_table_medium)
```


```{r}
model_log_bm_f3y_table_medium[["anova_table"]] %>% 
  filter(y %in% net_var_bm) %>%
  select(-mod_summary_table) %>%
  format_anova_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the temporal trends of 
      community biomass and the temporal trends of the network structure."
    ),
  label = "tab:aov-bm"

  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_rich_f3y_table_medium[["anova_table"]] %>% 
  filter(y %in% net_var_rich) %>%
  select(-mod_summary_table) %>%
  format_anova_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the temporal trends of species
      richness and the temporal trends of the network structure."
    ),
  label = "tab:aov-rich"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_bm_f3y_table_medium$reg_table %>% 
  filter(y %in% net_var_bm) %>%
  format_reg_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of community biomass and the temporal trends
      of the network structure."),
  label = "tab:reg-bm"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_rich_f3y_table_medium$reg_table %>%
  filter(y %in% net_var_rich) %>%
  format_reg_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of species richness and the temporal trends of
      the network structure."
    ),
  label = "tab:reg-rich"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
rsq %>%
  rename(
    Response = y, Explicative = x, 
    `Squared R` = r.squared, `Adjusted squared R` = adj.r.squared
  ) %>% 
  select(Explicative, Response, everything()) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Squared and adjusted squared R for linear models of spatial relationships."),
  label = "tab:rsq"
      ) %>% # 
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```


### Spatial

```{r}
loadd(tab_sp_anova)
```


```{r}
tab_sp_anova$log_bm_std %>%
  filter(y %in% net_var_bm) %>%
  mutate(
    y = str_replace_all(y, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the spatial variation of community
      biomass and the one of network structure."),
  label = "tab:aov-bm-sp"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
tab_sp_anova$log_rich_std %>%
  filter(y %in% net_var_rich) %>%
  mutate(
    y = str_replace_all(y, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the spatial variation of species
      richness and the one of network structure."),
  label = "tab:aov-rich-sp"
      ) %>% # 
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```


```{r}
table_rsq_sp <- map2(rsq_sp_mod, names(rsq_sp_mod),
  ~mutate(.x, Explicative = .y) %>%
    select(Explicative, Response, Marginal, Conditional)
) %>%
do.call(rbind, .)
rownames(table_rsq_sp) <- NULL

table_rsq_sp %>%
  filter(Explicative %in% c("log_rich_std", "log_bm_std")) %>%
  mutate(
    Explicative = str_replace_all(Explicative, var_replacement()),
    Response = str_replace_all(Response, var_replacement())
  ) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Marginal and conditional squared R for spatial models."),
  label = "tab:rsq-sp"
      ) %>% # 
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")

```

