---
title: "More than space for time: revealing the tight links constraining the temporal dynamics of network structure"
author: "Alain Danet, Maud Mouchet, Loubna El Madouri, Colin Fontaine (ordre non fixé)"
self_contained: yes
date: "`r Sys.Date()`"
tables: yes
bibliography: references.bib 
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    math: katex
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE 
)
```


```{r, results = FALSE}
library(drake)
library(tidyverse)
library(magrittr)
library(cowplot)
library(viridis)
library(kableExtra)
library(sf)
mypath <- rprojroot::find_package_root_file 
source(mypath("R/variable_shortcut.R")) # Define your custom code as a bunch of functions.
source(mypath("R/misc.R"))
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

mytheme <- theme_cowplot() +
background_grid()

theme_set(mytheme)
```

# Methods

## Data selection

## Food-web inference 

Because we had few informations about trophic interactions between resources, we
selected only the fish-fish interactions in subsequent analysis.

## Food-web and community structure

We characterized food-webs by its connectance, describing the degree of
generalism in a network [@dunne_network_2006, @delmas_analysing_2019]. It is
computed as the ratio between the actual number of links and the number of
potential links ($C = \frac{L}{S(S-1)}$, with $L$ being the number of links and
$S$ the number of trophic species). We also computed the average trophic level,
weighted by the biomass of the trophic species. The trophic level of a trophic
species is computed recursively as 1 added to the mean trophic level of the
preys that it consumes.

We described community structure by its total biomass, species richness and the
evenness of the number of individual and the amount of biomass across species. The evenness was
quantified with the Pielou index, computed as the Shannon diversity index
divided by the number of species ($P = \frac{H'}{N}$, with $H'$ being the
Shannon diversity index and $N$ the number of species).

```{r}
loadd(com_analysis_data)
```

## Classification of temporal trajectories

We characterized the temporal trajectories of network and community structure at
each site. We used a method based on second order polynomial which allows to
assess both the direction and the monotony of temporal trends
[@rigal_method_2020].

- Why do we want to classify temporal trends?
- How do we select station for each variable?

## Spatial  


# Result


Overall, we found no significant effect of the temporal gain or losses of total
biomass and species richness on the relationship between the temporal trends of
community structure and that of biomass and species richness (slope X, Table X).

## Community structure and biomass

We found a significant positive relationship between the temporal trends of total biomass from
one side and species richness, average trophic level, connectance from the other
side (slopes XX, Figure X, Table X), meaning that they increased in time when
the total biomass increased in time and respectively that they decreased in time
when the total biomass decreased in time. 

We found that a significant negative relationship between the temporal trends of
total biomass and that of the pielou of biomass (slopes XX, Figure X, Table X),
meaning that the pielou value increased in time when the total biomass decreased in time and
respectively that the pielou value decreased in time when the total biomass
increase in time. However, we found no relationship between the temporal trends of
total biomass and that of the pielou of individual.

## Community structure and species richness 

The temporal trends of total biomass, average trophic level, pielou of biomass,
pielou of individual had a positive relationship with that of species
richness (slopes XX, Figure X, Table X). However, the direct relationship
between the temporal trends of average trophic level and the one of species
richness was not significant after controling for total biomass temporal trends.

We also found that the relationship between the temporal trends of pielou of
individual and connectance and that of species richness was dependant of the
overall species richness of the community (Figure X, Table X). The relationship
between temporal trends of pielou of individual and that of species richness
was more positive as the community contained more species (+ XX by species by
square meter). While the relationship between temporal trends of pielou of
individual and that of species richness was more negative as the community
contained more species.

# Discussion

- Main results:
  - different mechanisms for richness and biomass
  - space for time subtitution works for biomass and tlvl but not for
    connectance

## Temporal dynamics confirms space for time substitution BEF

The temporal dynamic of the species richness was positively linked to that of
biomass. In non-temporal data, this result was already found in streams
[@woods_testing_2020; @danet_species_nodate] but also in grasslands salt marches
and forests [@hector_plant_1999; @tilman_biodiversity_2014;
@wu_relationship_2015; @li_relationship_2018; but see @grace_integrative_2016]. Therefore,
our results confirm BEF prediction works also in time.  

*From the previous manuscript*: the positive relationship of species richness on total
biomass might be due to resource use complementarity [@carey_determining_2011],
which is held by niche differentiation [@loreau_biodiversity_1998;
@loreau_partitioning_2001] or to the higher probability of getting high biomass
species with higher species richness [@loreau_biodiversity_2001].

We found the temporal dynamic of connectance was negative associated, but
weakly, with that one of species richness as found in most empirical foodweb
[@dunne_network_2006]. The relationship is very weak in species rich commuties
and more negative for species poor commuties. An explanation might be that
species-rich communities already contains a significant number of piscivores, which have the
most links whereas species poor communites contains few piscivores. 

The temporal dynamic of the average trophic level had no relationship with the
one of species richness. It is surprising because one can imagine that loss and
gain of species would reveal assembly/disassembly mechanisms in terms of trophic
structure. However, we found that when species richness increases, the
distribution of biomass and individuals among species become more even in the
community, meaning that dominance decrease. Species richness has often been
found to be positively or negatively related to individual eveness
[@soininen_relationship_2012; @maureaud_biodiversity_2019].

 
## Biomass temporal dynamics is linked to the top trophic level

We further found that the temporal dynamic of the average trophic level was positively
linked to that of biomass. Increase  of average trophic level can be associated
to either gain of biomass in the highest trophic level nor losses of biomass in
the lowest trophic. In our case, such gain or losses of average trophic level is
certainly associated to the loss or the gain of the biggest individuals. Because
it seems unlikely that a community gain or loss biomass while respectively
losing or gaining individuals. Pielou index temporal dynamics further confirm
this interpretation. 

We found that the pielou of biomass decrease through time
as total biomass decrease and reversely, meaning that biomass distribution
across species respectively became less and more even when total biomass
decrease and increase. The structuration in size class of the community might
explain this pattern.

Finally, we found no relationship between the temporal
dynamics of pielou based on indivual number and that one of biomass, confirming
that the temporal trends of total biomass in our study is linked to few big
individuals. @maureaud_biodiversity_2019 found negative relationship between
biomass and eveness of indivual in marine ecosystem. One explanation is that
marine ecosystem studied in [@maureaud_biodiversity_2019] are much larger than
the stream communities studied in this study. 

We further found that the temporal dynamic of connectance was positively
linked to that one of total biomass, meaning that connectance increases through
time in a given site when total biomass increases through time and reversely.
This is in line with the fact that the fishes located at higher trophic level
also display a larger number of links as the size of the predation window
increases with the size of the fishes. This is because the predation window of
freshwater fish species is highly nested.

##  Biomass and richness variation are not the same process 

Our results indicate that biomass trends are linked to few big individuals while
richness trends are linked to overall shift in dominance in communities. This
results has profound implications for conservation. As more and more studies
report biomass and richness temporal dynamics [@hallmann_more_2017;
@ceballos_biological_2017], it is important to note that they might not be
equivalent in terms of consequences on the structure of the community. Further
studies should investigate several dimensions of community structure because it
drives many aspects of ecosystem functioning. 

## Biomass and richness gains and losses are symmetric processes in terms of community structure

We found no case in which gain or losses of biomass and richness lead to
different relationship between the temporal dynamic of community structure and
the one of biomass and species richness. We could have imagine that
extinction/colonisation processes or immigration/extinction debt could have lead
to different relationships.

## Space for time substitution does not always hold 

We found that total biomass was linked positively related to species richness
both in space and in time, indicating that space for time might be use. In the
same way, we found a positive positive relationship between average trophic
level and total biomass both in time and in space. However, it was not the case
for connectance and average trophic level that were respectively weakly or not
linked to species richness in time whereas our result shows a strong negative
relation in space. Moreover, connectance displayed a strong positive
relationship (move to results?) with biomass in time but not in space. 

Space for time substitution is a widely
used tool in ecology [@pickett_space-for-time_1989; @blois_space_2013;
@damgaard_critique_2019]. However, the drivers of spatial variation might not
be the ones that drive community variation in time. The successional processes
driving the assembly or the disassembly of communities might not be reflected in
spatial gradient.

## Conclusion

We showed that BEF works in time but that richness and biomass temporal trends through
time relates on different ecological processes inside communities. We further
found that space for time subtitution does not always work. 


# References  {-}

<div id="refs"></div>

# Figures {-}

```{r}
loadd(p_fig1_2)
p_fig1_2
```

