---
title: "More than space for time: revealing the tight links constraining the temporal dynamics of network structure"
author: "Alain Danet, Maud Mouchet, Loubna El Madouri, Colin Fontaine"
self_contained: yes
date: "`r Sys.Date()`"
tables: yes
bibliography: references.bib 
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    math: katex
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE 
)
```


```{r, results = FALSE}
library(drake)
library(tidyverse)
library(magrittr)
library(cowplot)
library(viridis)
library(kableExtra)
library(sf)
mypath <- rprojroot::find_package_root_file 
source(mypath("R/variable_shortcut.R")) # Define your custom code as a bunch of functions.
source(mypath("R/misc.R"))
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

mytheme <- theme_cowplot() +
background_grid()

theme_set(mytheme)
```

# Result


Overall, we found no significant effect of the temporal gain or losses of total
biomass and species richness on the relationship between the temporal trends of
community structure and that of biomass and species richness (slope X, Table X).

## Community structure and biomass

We found a significant positive relationship between the temporal trends of total biomass from
one side and species richness, average trophic level, connectance from the other
side (slopes XX, Figure X, Table X), meaning that they increased in time when
the total biomass increased in time and respectively that they decreased in time
when the total biomass decreased in time. 

We found that a significant negative relationship between the temporal trends of
total biomass and that of the pielou of biomass (slopes XX, Figure X, Table X),
meaning that the pielou value increased in time when the total biomass decreased in time and
respectively that the pielou value decreased in time when the total biomass
increase in time. However, we found no relationship between the temporal trends of
total biomass and that of the pielou of individual.

## Community structure and species richness 


The temporal trends of total biomass, average trophic level, pielou of biomass,
pielou of individual had a positive relationship with that of species
richness (slopes XX, Figure X, Table X).

We also found that the relationship between the temporal trends of pielou of
individual and connectance and that of species richness was dependant of the
overall species richness of the community (Figure X, Table X). The relationship
between temporal trends of pielou of individual and that of species richness
was more positive as the community contained more species (+ XX by species by
square meter). While the relationship between temporal trends of pielou of
individual and that of species richness was more negative as the community
contained more species.

# Discussion


##

[@danet_species_nodate]

# References  {-}

<div id="refs"></div>

# Figures {-}

