---
title: "Community biomass and species richness temporal trends reveal contrasting assembly and disassembly processes in natural food-webs"
author: Alain Danet, Loubna El Madouri, Maud Mouchet, Elisa Thébault and Colin Fontaine
date: \today
output:
  bookdown::pdf_document2:
    fig_caption: true 
    keep_tex: true
    toc: true
  bookdown::word_document2:
fontsize: 12pt
header-includes:
   - \usepackage{natbib}
   - \usepackage{float}
   - \usepackage{multirow}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
number_sections: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE,
  fig.path="figures/"
)
```

- Tentative titles:
  - How food-webs assembly and disassembly through time in natural settings?
    Lessons from freshwater fishes
  - Relationships among temporal trends of food-web structure, species richness
    and community biomass reveal contrasting assembly
    and disassembly processes
  - Temporal trends in food web structure according to richness and biomass
    reveal contrasting assembly and disassembly processes  

```{r, results = FALSE}
library(drake)
library(tidyverse)
library(magrittr)
library(cowplot)
library(viridis)
library(kableExtra)
library(sf)
mypath <- rprojroot::find_package_root_file
source(mypath("R/variable_shortcut.R")) # Define your custom code as a bunch of functions.
source(mypath("R/misc.R"))
source_dir(get_mypath("R")) # Define your custom code as a bunch of functions.

mytheme <- theme_cowplot() +
background_grid()

theme_set(mytheme)
options(knitr.table.format = "latex")
```

```{r}
loadd(rsq_table_bm_rich_mono_stable_trends)
loadd(reg_table_bm_rich_mono_stable_trends)
```

```{r}
net_var_bm <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
      "piel_nind")
net_var_rich <- c("log_bm_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
      "piel_nind")
```

```{r}
loadd(slope_com_var_no_covar, st_mono_trends_stable_rich_bm)
loadd(range_data)
```
```{r}
nb_st <- unique(slope_com_var_no_covar$station) %>% length
rm(slope_com_var_no_covar)
nb_st_rich_bm <- st_mono_trends_stable_rich_bm %>% length
```

# Introduction

## Trends of biodiversity need to be assessed at multiple facets 

Multiple studies reported dramatic declines of population and community biomass
[@ceballos_biological_2017; @hallmann_more_2017; @albano_native_2021], as well
as decrease in species richness [@barnosky_has_2011; @newbold_global_2015] but
also recent studies reported non significant temporal trends in species richness
[@vellend_global_2013; @dornelas_assemblage_2014; @blowes_geography_2019], total
abundance [@klink_meta-analysis_2020], high turnover in species composition
[@dornelas_assemblage_2014; @blowes_geography_2019]. Unfortunately, studies
often focus on the temporal trend of one dimension of biodiversity
[@hallmann_more_2017; @klink_meta-analysis_2020, but see 2 in
@dornelas_assemblage_2014; @blowes_geography_2019]. However biodiversity is a
multidimensional concept and the functioning of ecosystem depends ultimately on
several dimensions of biodiversity, such as species richness, evenness and
functional composition^[1]  [@cardinale_biodiversity_2012; @duffy_why_2009], the
documentation of the trend of one biodiversity facet is likely insufficient to
understand changes in community structure and ultimately predict their
consequences on ecosystem functioning.

[^1]: Commentaire de Colin: *je pense qu'il faut lister les facet de biodiv qu'on
va etudier. sans forcement s'y limiter?* Ici je pense que la composition en role
trophique rentre dans "functional composition" sans rentrer dans le détail.

## Current knowledge mainly comes from space-for-time substitution 

Current knowledge on the links among the different facets of biodiversity mainly
comes from spatial comparison [@dunne_network_2006;
@soininen_relationship_2012; @grace_integrative_2016; @danet_species_nodate],
which is used to predict how community structure will change in time, under the
assumption of the space-for-time substitution. It supposes a homology between
variations in space and in time, i.e. that spatial sequences correspond
to temporal sequences. This method have raised criticisms
[@damgaard_critique_2019], with studies showing analogous patterns in space and
time [@blois_space_2013] or not [@johnson_testing_2008;
@adler_contrasting_2007]. Spatial turnover of species composition, dispersal
limitation, disturbance and stochastic processes have been hypothesised to be
responsible for the non-compliance of space-for-time substitution
[@adler_contrasting_2007; @blois_space_2013]. The recent increase in the availability
of temporal monitoring of ecological communities makes possible to address
biodiversity trends for multiple facets. 

## Temporal variation of food-webs is largely unknown

More dramatic is that the temporal trends of biodiversity generally neglect
species interactions. Although species interactions determine for a large part
community composition, species coexistence and ecosystem functioning
[@chesson_mechanisms_2000; @thebault_food-web_2003; @oconnor_general_2017].
Furthermore, species interactions can imply tremendous secondary extinctions
[@paine_note_1969; @dunne_network_2002]. In food-webs, spatial comparisons in
empirical and theoretical studies generally reported that trophic level
positively scales to community biomass [@wang_biodiversity_2018;
@danet_species_nodate]. Trophic level has also been shown to stabilise the
temporal variation of community biomass [@shanafelt_stability_2018;
@danet_species_nodate]. Connectance, which measures the degree of generalism in
a network, was shown to increase robustness to extinction [@dunne_network_2002].
However, the temporal variation of food-web structure is largely unknown
[@kortsch_disentangling_2021]. Food-web temporal variation are often reported
across small time-steps [@warren_spatial_1989; @pecuchet_novel_2020;
@kaartinen_high_2012]. Our knowledge on the variability of food-web structure in
time are even more scarce and particularly how those temporal variations are
linked to the temporal variations of other aspects of biodiversity such as
species richness and community biomass. Spatially, connectance has been shown to
be negatively related to species richness in empirical food-webs [reviewed in
@dunne_network_2006]. Connectance has been shown to scale positively or
negatively with community biomass in theoretical models
[@thebault_food-web_2003; @poisot_trophic_2013]. Average trophic level was
previously shown to scale negatively with species richness
[@danet_species_2021].  In order to improve our knowledge on the consequences of
biodiversity trends such as community biomass and species richness, it is thus
crucial to assess how biomass and species richness temporal trends are
associated to temporal trends of food-web structure. 

Even how the temporal trends of community biomass are related to temporal
trends of species richness is still questionned in natural settings, especially
in food-webs. Our knowledge on the relationships between food-web structure and
other facets of biodiversity often comes from the comparison of food-web
snapshots along spatial gradient, raising the question of the validity of
space-for-time substitution to infer consequences of species richness and
community biomass variations on food-web structure.

The increasing availability ecological temporal series and the development of
methods to reconstruct food-webs [@bonnaffe_comparison_2021;
@gravel_inferring_2013; @danet_species_nodate] makes possible to assess the
relationships among several biodiversity facets, including food-web structure.
We used the standardized monitoring of fish freshwater communities on the period
1995-2018 over France, documenting the individual size of fishes in
400 sites during ten years or more. We then reconstruct around 4000 food-webs
based on allometric relationships and food diet data. We questionned i) how
temporal trends of food-web structure are  linked to trends of community biomass
and trends in species richness? ii) Are the relationships observed in time the
same as those observed in space, i.e. is the space-for-time substitution valid? 

---
## Variations of community biomass and species richness are predicted to affect community structure
#Changes of species richness and community biomass are indeed
#predicted to affect community structure. The positive link between biodiversity
#and ecosystem functioning in experimental studies predict that loss and
#gain of species richness should respectively result in loss and gain of
#community biomass [@tilman_biodiversity_2014; @pennekamp_biodiversity_2018]. But
#this relation is not always found in natural settings [@grace_integrative_2016;
#@li_relationship_2018; @maureaud_biodiversityecosystem_2019].
#
#Variations of species richness can also result in variation of evenness, i.e.
#equitability of species abundances or biomasses. Meta-analysis reported that
#higher evenness of abundances is linked to higher plant biomass in grasslands
#and primary productivity in marine ecosystems [@soininen_relationship_2012].
#Furthermore, studies reported that higher evenness plays a role of insurance in
#face of perturbations [@wittebolle_initial_2009]. Indeed, most studies reported
#positive relationship between species richness and evenness, but also neutral
#and negative ones [@soininen_relationship_2012; @ma_species_2005;
#@maureaud_biodiversityecosystem_2019].
## Variations of community biomass and species richness are predicted to affect food-web structure
---


# Methods

## Data

We used a monitoring of freshwater fishes conducted all over France and
conducted by the Office Français de la Biodiversité (OFB, previously known as
ONEMA and AFB). The sampling protocols were standardized since 1995 and a
complete description of the sampling process can be found in
@danet_species_nodate (main text and appendixS2). The fishes are sampled using
electrofishing all across the streams in shallow streams and over the bank by
boat in deeper streams. All the fishes are counted and the bodysize of fishes are
recorded for a sample of them, enabling the estimate the distribution of
individual bodysize by species for each sampling [@bonnaffe_comparison_2021;
@danet_species_nodate].

## Data selection

We selected the sites that have been monitored at least 10 years on the
1995-2018 period, with the same sampling protocol over time. We selected
one sampling a year by site. In each site, we ensured low temporal heterogeneity
in sampling period by selecting sampling that were performed in the same period,
leading to a mean standard deviation of sampled month in each site of three
weeks [@danet_species_nodate]. Those steps leads to the selection of 
`r nb_st` sites (Figure \@ref(fig:matmet)A).

## Biomass 

We first inferred the body mass of each fish individual considering an allometric
law, $B_i = 0.01 \times l_i^{3.03}$, $B_i$ being the biomass expressed in gram and $l_i$ the
body length of the individual $i$ expressed in millimetres  [@froese_cube_2006]. Then the
biomass of each species and community biomass were obtained by summing the body
mass of individuals. Finally, the biomass was reported to the sampled surface
(in $m^2$) to account for sampling effort.
 
## Food-web inference 

We inferred food-web structure in two steps [@bonnaffe_comparison_2021;
@danet_species_2021]: (1) we first computed the metaweb, describing the
potential trophic interactions among all size classes species, (2) then we
extracted each yearly snapshot of food-webs by extracting species size classes
and their interactions according to their presence in a given sampling event.
 
We inferred the metaweb according to ontogenic diet data and body size
[@gravel_inferring_2013; @poisot_structure_2016; @brose_predator_2019;
@bonnaffe_comparison_2021; @danet_species_2021]. The method is extensively
described in @bonnaffe_comparison_2021 and @danet_species_2021. The food diet of
stream fishes changes along their life cycle or stage, therefore according to
their body size. Each fish species was divided in nine size classes, named
"trophic species", equally distributed in their observed body size range. Thus,
a trophic species is a group of individuals of the same species and size class
that are expected to share the same preys and predators because trophic
interactions are largely determined by predator-prey size ratio
[@brose_allometric_2006]. We also added seven nodes present in the ontogenic
food diet database: detritus, biofilm, phytoplankton, zooplankton, macrophages,
phytobenthos and zoobenthos.  The resulting metaweb contained 45 fish species
divided into nine size classes plus 7 resource nodes, summing up to 412 nodes.
Consideration of size classes, i.e.  trophic species instead of species,
improves inference of trophic interactions [@jennings_weak_2001].

We determined the feeding interactions of trophic species according to their
species identity and their body size. The diet database described two or three
life stages by fish species, each one being delimited by body size
[@bonnaffe_comparison_2021; @danet_species_nodate]. The ontogenic fish diet
database was filled according to fishbase (Froese et al. 2021) and literature
[@bonnaffe_comparison_2021; @danet_species_nodate].

The feeding interactions among fishes were based on the body size ratio
between predators and preys. We defined the predation window of a
piscivorous trophic species as 3% to 45% of its midpoint
[@mittelbach_ontogeny_1998; @claessen_impact_2002; @hart_handbook_2008].  A
trophic link was defined between the piscivorous trophic species and all the
trophic species whose midpoint in body size range was included in the predation
window.  The fish-resource trophic links were set between the trophic species
and the resources nodes according to the food items of their size class.
Finally, the feeding interactions between resources were defined according to the
literature [@allan_stream_2007; @hart_handbook_2008].

## Community and food-web structure

At each site, yearly food-webs were described by their community biomass,
species richness and the evenness of biomass across species. The evenness was
quantified with the Pielou index, computed as the Shannon diversity index
divided by the number of species ($P = \frac{H'}{N}$, with $H'$ being the
Shannon diversity index and $N$ the number of species). Yearly food-web
structure was described by their connectance, describing the degree of
generalism in a network [@dunne_network_2006; @delmas_analysing_2019]. It was
computed as the ratio between the number of actual links and the number of
potential links ($C = \frac{L}{S(S-1)}$, with $L$ being the number of links and
$S$ the number of trophic species). We also computed the average trophic level,
weighted by the biomass of the trophic species. The trophic level of a trophic
species was computed recursively as 1 added to the mean trophic level of the
preys that it consumes [@herendeen_ecological_2008].


## Temporal trends of food-web 

To characterize the links among the temporal trends of network and community
structure and the temporal trends of community biomass and species richness, we
characterized the temporal trajectories of food-web structure at each site. We
modeled a linear relationship between food-web structure and
time with a second order polynome, which allows to assess both the direction and the monotony of temporal
trends [@rigal_method_2020]. We selected the sites that displayed monotonic
trends for these variables, i.e. the ones for which the second order polynomial
term was non significant according to t-tests, to avoid the inclusion of many
types of biomass and species richness trends (i.e. accelerating, decelerating,
etc...), . Over the `r nb_st` monitored sites, the selection procedure resulted in 
`r nb_st_rich_bm` sites for community biomass and species richness analysis.
However, the results were robust to the inclusion of non monotonic trends (Fig.
SXX).

There was a clear relationship between the size of the communities and their
temporal dynamics. Communities that displayed low community biomass at the
beginning of their monitoring tend to display a biomass increase through time
and reversely, we observed the same pattern for species richness. We
log-transformed (natural logarithm) community biomass and species richness to model their trends,
which decreased the former effect (Fig. SXX). Temporal
trends of community biomass and species richness were thus expressed in rate of
change by year.


## Spatial

To assess the validity of the space-for-time substitution hypothesis, we
compared the relationships among food-web structure in time to the ones observed
in space. To do so, we selected the same sites that were used
for the temporal analysis. We summarised temporal series of each station by the
median value over time of each facet of food-web structure described above.
 
# Statistical analysis

## Relationships among temporal trends 

We modelled the relationships among the temporal trends of food-web structure
($dN$), that is connectance, average trophic level and evenness of biomass, and
the temporal trends of community biomass ($dB$) and species richness ($dR$) with
Ordinary Least Squares. The simultaneous assessment of the
effects of species richness and community biomass allows to tease apart their
respective effect on food-web structure.

$dN_j = \alpha + \beta_1dB_j + \beta_2dR_j + \epsilon_j$

With:

  - $dN$: temporal trends of food-web structure: connectance, average trophic
    level and evenness of biomass across species
  - $dB$: temporal trend of ($\log_e$) community biomass
  - $dR$: temporal trend of ($\log_e$) species richness
  - $j$: the site
  - $\alpha$: intercept 
  - $\beta$: slope 
  - $\epsilon$: gaussian error

In order to control for the uncertainties of the estimated temporal trends, each
temporal trend was weighted by the inverse of the product of the standard errors
of the estimated trends, i.e. estimated slopes for the response and the
explicative variables ($w_j = \dfrac{1}{s_{r_j} s_{e,j}}$, $w_j$ being the
weight, $s_{r_j}$ and $s_{e_j}$ being respectively the standard errors on the
temporal trends of the response and explicative variables). We also included a
statistical model including the interaction between the temporal trends of
species richness and community biomass (i.e.  adding $\beta_3dB_jdR_j$), the
results are presented in supplementary material (Fig.  SXX). To model the
relationships between the temporal trends of community biomass and the one of
species richness, we built the model as $dB_j = \alpha_j + \beta_1dR_j +
\epsilon_j$.

  

## Relationships along spatial gradient 

Spatial variation of food-web structure are partly driven by environmental gradients, so
we controlled relationships among variables by adding two PCA axis
synthesizing respectively (1) stream gradient from upstream to downstream and
(2) enrichment (Fig. \@ref(fig:matmet)). Enrichment was characterized by the
average Biological Oxygen Demand [BOD, @mallin_factors_2006][^2]. We further
added a random effect of the hydrographic basin on the intercept.

[^2]: commentaire de colin: il faudrait introduire spatial gradient des l'intro
et cette partie est plutot sur les relationships among spatial gradient of biodiv facets
 
$N_j = \alpha + \beta_1B_j + \beta_2R_j + \beta_3E_{1,j} + \beta_4E_{2,j} + \epsilon_j + \epsilon_{\alpha|i}$ 

With:

  - $N_j$: median food-web structure 
  - $B_j$: median community biomass ($g.m^-2$) 
  - $R_j$: median species richness ($m^-2$) 
  - $E_{1,j}$: First PCA axis 
  - $E_{2,j}$: Second PCA axis
  - $\epsilon_{\alpha|i}$: random effect of the hydrographic basin
    $i$ on $\alpha$

To model the relationships between community biomass and species richness along
the spatial gradient, we built the equation as $B_j = \alpha + \beta_1R_j +
\beta_3E_{1,j} + \beta_4E_{2,j} + \epsilon_j$.

In order to compare the magnitude of the effects of community biomass and
species richness in both temporal and spatial models, we computed standardized
slopes ($r_{\delta}$) and their associated standard errors as $r_{\delta} =
\beta\frac{s_x}{s_y}$.  With $\beta$ being the unstandardised slope, $s_x$ and
$s_y$ the standard deviation of the explicative and response variables.

All the statistical models displayed low multicollinearity (Variance inflation
factor < 3, Table SXX).  We visually inspected the residuals of the linear models.

```{r}

fig_mat_cap <- paste0("Using  sites of stream fishes in French streams that
  have been monitored at least 10 years, 1) we infered the food-web at each site
and each sampling event based on ontogenic food diet information for each
species and predator-prey body size ratio. 2) We computed the temporal trends
and the median of community biomass, species richness, connectance, average
trophic level and evenness of biomass at each site. 3) We then assessed the
relationships among a) temporal trends of food-web structure. We also assessed
the spatial relationships among median food-web structure while controlling for
the environmental gradient with two axis of a rotated PCA. The first axis of the
PCA is related to the stream gradient from upstream to downstream while the
second is related to enrichment (BOD) and site altitude.")

```

```{r matmet, fig.cap=fig_mat_cap, out.width="80%"}
knitr::include_graphics(get_mypath("figures", "mat_met_inkscape.pdf"))
```

# Results

```{r}
loadd(rsq_sp_mod, summary_table, sp_models, model_summary)

loadd(rsq_table_bm_rich_mono_stable_trends, sp_rsq_table_bm_rich_mono_stable_trends)

loadd(rigal_classification)
```

```{r}
log_trends_percent <- rigal_classification %>%
  unnest(classif) %>%
  filter(variable %in% c("log_bm_std", "log_rich_std")) %>%
  select(variable, station, linear_slope, linear_slope_strd_error) %>%
  mutate(
    slp_percent = round((exp(linear_slope) - 1) * 100),
    std_err_percent = round((exp(linear_slope_strd_error) - 1) * 100)
  )
resume_log_trends <- log_trends_percent %>%
  group_by(variable) %>%
  summarise(
    mean = mean(slp_percent, na.rm = TRUE),
    sd = sd(slp_percent, na.rm = TRUE))
```


```{r}
class_trends_bm_rich <- rigal_classification %>%
  filter(variable %in% c("log_bm_std", "log_rich_std")) %>%
  unnest(classif) %>%
  select(variable, station, direction, acceleration, shape_class)

res_trends <- class_trends_bm_rich %>%
  filter(acceleration == "constant") %>%
  group_by(variable, direction) %>%
  summarise(n = n()) %>%
  group_by(variable) %>%
  mutate(total = sum(n), percent = round(n / sum(n) * 100))

x_var <- c("log_bm_std", "log_rich_std")
stable_st_var <- map(x_var,
  ~class_trends_bm_rich[
    class_trends_bm_rich$variable == .x &
    class_trends_bm_rich$direction == "stable",
      ]$station
)
names(stable_st_var) <- x_var

#sum(stable_st_var[["log_bm_std"]] %in% stable_st_var[["log_rich_std"]] == TRUE) / length(stable_st_var[["log_bm_std"]])

#sum(stable_st_var[["log_rich_std"]] %in% stable_st_var[["log_bm_std"]] == TRUE) / length(stable_st_var[["log_rich_std"]])
```

```{r}
loadd(std_table_bm_rich_mono_stable_trends)
std <-
  std_table_bm_rich_mono_stable_trends %>%
  mutate(
    type = recode(type, spatial = "sp", temporal = "tps"),
    response = recode(response, log_bm_std = "bm", log_rich_std = "rich", ct_ff
      = "ct", piel_bm = "p_bm", piel_nind = "p_n", w_trph_lvl_avg = "tlvl"),
    term = recode(term, log_bm_std = "bm", log_rich_std = "rich")
    ) %>%
  rename(t = type, rep = response, sest = std_estimate) %>%
  mutate_at(vars(sest, stdse), ~round(.x, 2))
tps_bm <- std %>%
  filter(t == "tps", term == "bm")

tps_bm_sest <- tps_bm$sest
names(tps_bm_sest) <- tps_bm$rep
```

```{r}
tps_r <- std %>%
  filter(t == "tps", term == "rich")

tps_r_sest <- tps_r$sest
names(tps_r_sest) <- tps_r$rep
```

```{r}
sp_b <- std %>%
  filter(t == "sp", term == "bm")
sp_b_sest <- sp_b$sest
names(sp_b_sest) <- sp_b$rep

sp_r <- std %>%
  filter(t == "sp", term == "rich")
sp_r_sest <- sp_r$sest
names(sp_r_sest) <- sp_r$rep
```


```{r}
rsq_piel_nind <- rsq_table_bm_rich_mono_stable_trends %>%
  filter(Response == "piel_nind") %>%
  .$R.squared %>%
  round(., 3)

rsq_tlvl <- rsq_table_bm_rich_mono_stable_trends %>%
  filter(Response == "w_trph_lvl_avg") %>%
  .$R.squared %>%
  round(., 3)

rsq_tlvl_sp <- sp_rsq_table_bm_rich_mono_stable_trends %>%
  filter(Response == "w_trph_lvl_avg") %>%
  .$Conditional %>%
  round(., 3)

rsq_piel_bm_sp <- sp_rsq_table_bm_rich_mono_stable_trends %>%
  filter(Response == "piel_bm") %>%
  .$Conditional %>%
  round(., 3)
```
Over the sampling sites in the dataset, we found that
`r res_trends[res_trends$variable == "log_bm_std", ]$total[1]` stations displayed monotonic trends for biomass. Among them, 
`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "stable", ]$percent`%
were classified as stable,
`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "decrease", ]$percent`%
as decreasing,
`r res_trends[res_trends$variable == "log_bm_std" & res_trends$direction == "increase", ]$percent`%
as increasing. Regarding the species richness, we found that
`r res_trends[res_trends$variable == "log_rich_std", ]$total[1]` stations displayed monotonic trends.
`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "stable", ]$percent`%
were classified as stable,  
`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "decrease", ]$percent`%
as decreasing, and 
`r res_trends[res_trends$variable == "log_rich_std" & res_trends$direction == "increase", ]$percent`% as increasing.

Overall, we found high heterogeneity in the explicative power of statistical
models linking temporal dynamics of food-web structure, evenness of biomass  and the one of community
biomass and species richness spanning from $R_{adj}^2= `r rsq_piel_nind`$ for
the evenness of abundances to $R_{adj}^2= `r rsq_tlvl`$ for average trophic
level (Table SXX). The models over the spatial gradient were more performant, with
$R_{cond}^2$ varing from $`r rsq_tlvl_sp`$ to $`r rsq_piel_bm_sp`$ (Table
SXX), $R_{cond}^2$ being the $R^2$conditional to the random effect. 

---
#Overall, we found no significant effect of the temporal gain or losses of
#communinity biomass biomass and species richness on the relationship between the
#temporal trends of community structure and that of biomass and species richness
#(Table \@ref(tab:aov)).
---

```{r}
loadd(sp_fig1_2_bm_rich_mono_stable_trends,
  pred_bm_rich_mono_stable_trends)

fig1_2 <- get_plot_rich_bm(
  predict_plot = pred_bm_rich_mono_stable_trends,
  get_list = TRUE,
  rm_legend = FALSE,
  bm_x = "log_bm_std",
  bm_y = c("ct_ff", "w_trph_lvl_avg"), #, "piel_nind"
  rich_y = c("ct_ff", "w_trph_lvl_avg", "log_bm_std"), #, "piel_nind"
  rich_x = "log_rich_std"
  )
p_bm <- fig1_2$bm

p_sp_bm <- sp_fig1_2_bm_rich_mono_stable_trends$bm[c("log_rich_std", "ct_ff", "w_trph_lvl_avg")]
```



```{r}
fig_bef_cap <- paste0(
  "Relationship between the temporal trends of community biomass 
  and the one of species richness. Red line correspond to the predictions of the
  linear models. The lines surrounding points display the standard error
  associated to the temporal trends. The histograms display the distribution of
  response and predictive variables."
)
```

```{r}
library(ggExtra)
coeff_bef <- c(
  rsq = rsq_table_bm_rich_mono_stable_trends %>%
    filter(Response == "log_bm_std") %$%
    unlist(.[, c("R.squared")]),
  reg_table_bm_rich_mono_stable_trends %>%
    filter(response == "log_bm_std", term == "log_rich_std") %$%
    unlist(.[, c("estimate", "std.error", "std_estimate", "stdse")])
  ) %>%
round(., 2)

beta_rsq <- function(
  rsq = NULL,
  beta = NULL,
  se = NULL) {

  if (!is.null(rsq)) {

    tmp <- "paste(
    beta, \" (s.e.) \", \" = \",
    mybeta, \" (\", myse, \"), \",
    italic(R)^2, \" = \", myrsq
    )"
str_replace_all(tmp,
  c(
    "myrsq" =  as.character(rsq),
    "mybeta" = as.character(beta),
    "myse" = as.character(se)
  )
)

  } else {

    tmp <- "paste(
    beta, \" (s.e) \", \" = \",
    mybeta, \" (\", myse, \") \" )"
str_replace_all(tmp,
  c(
    "mybeta" = as.character(beta),
    "myse" = as.character(se)
  )
)

  }


}

scale_xy_log_trends <- function(breaks = NULL, axis = "y", sep ="\n") {
  log_to_percent <- round((exp(breaks) - 1) * 100)
  labels <- paste0(breaks, sep, log_to_percent, " %")

  if(axis == "y") {
    fun <- scale_y_continuous
  } else {
    fun <- scale_x_continuous
  }

  fun(breaks = breaks, labels = labels)

}
```

```{r bef, fig.cap=fig_bef_cap, out.width="50%"}
lab_log_rich <- expression(atop("Log species richness ("*m^{-2}*")","trend slope (log / % per year)"))
lab_log_bm <- expression(atop("Log community biomass ("*g.m^{-2}*")", "trend slope (log / % per year)"))

p_bef <- fig1_2$rich$log_bm_std +
  annotate("text", x = .1, y = -.5, parse = T,
    label = beta_rsq(
      rsq = coeff_bef["rsq"],
      beta = coeff_bef["estimate"],
      se = coeff_bef["std.error"]
    )
   ) +
  labs(
    y = lab_log_bm,
    x = lab_log_rich
  ) +
scale_xy_log_trends(breaks = c(-.10, -.050, 0, .050, .10), axis = "x") +
scale_xy_log_trends(breaks = c(-.4, -.2, 0, .4, .2), axis = "y", sep = " / ")

```

We found a strong positive relationship between the temporal trends of community
biomass and the ones of species richness ($r_\delta = `r tps_r_sest["p_bm"]`$,
Fig. \@ref(fig:bef)), meaning that both temporal trends
had the same direction in average. At the sites 
where species richness decreased over time, community biomass also decreased
over time. On the other hand, at the sites where species richness increased over
time, community biomass also increased over time. Along the spatial gradient, we also
found a positive relationship between median community biomass and median
species richness, but half the strength as the temporal one
($r_\delta = `r sp_b_sest["rich"]`$).

The temporal trends of connectance were positively linked with the ones of
community biomass ($r_\delta = `r tps_bm_sest["ct"]`$), also meaning that both
temporal trends had the same direction in average. That is, the sites where
food-web connectance decreased over time also had community biomass that
decreased over time and reversely. It suggests that communities that decreased
in biomass over time loose generalist predators over time, as connectance
measures the degree of generalism, and reversely that communities
gaining biomass over time also gain generalist predators. Spatially, we also found
a positive relationship between median connectance and median species
richness ($r_\delta = `r sp_b_sest["ct"]`$). However, we did not observe
significant relationships between the temporal trends of connectance and the
ones of species richness (Fig. \@ref(fig:bmr)D) while we found a stong
negative relationship between median connectance and median species richness
along the spatial gradient
($r_\delta = `r sp_r_sest["ct"]`$, Fig. \@ref(fig:std)).

The temporal trends of average trophic level had a strong positive
relationship with the ones of community biomass 
($r_\delta = `r tps_bm_sest["tlvl"]`$, Fig. \@ref(fig:bmr)B), meaning
that sites where community biomass decreased over time, average trophic level
decreased over time and *vice versa*. It means that in communities loosing biomass
over time, the average biomass of the food-web moved down to lower trophic level
and *vice versa*. We also found a positive relationship between
median average trophic level and median community biomass in space, but half the strength 
as the temporal one ($r_\delta = `r sp_b_sest["tlvl"]`$, Fig. \@ref(fig:std)). The temporal trends of average
trophic level was unrelated to the ones of species richness. It suggests that in
communities either loosing or gaining species richness over time, the location of
average biomass along trophic level did not significantly change according to
species richnnes.  However, we found a strong negative relationship in space 
($r_\delta = `r sp_r_sest["tlvl"]`$, Fig. \@ref(fig:std)).

Evenness of biomass was negatively linked to community
biomass in time and in space 
($r_\delta = `r tps_bm_sest["p_bm"]`$ and $`r sp_b_sest["p_bm"]`$ resp.; Fig.
\@ref(fig:bmr)C, Fig. \@ref(fig:std)). Regarding time, it means that food-webs that
lost biomass over time also had a more even distribution of biomass across species over
time and *vice versa*. A similar reasoning applies in space. On the
other hand, we found a positive relationship between the temporal trends of
biomass evenness and the one of species richness (Fig. \@ref(fig:bmr)F,
$r_\delta = `r tps_r_sest["p_bm"]`$). We found the same relationship in space,
twice as strong however ($r_\delta = `r sp_r_sest["p_bm"]`$).


```{r}
fig_bm_cap <- paste0(
  "Relationship between community structure and community biomass. Left panel
  displays the relationships between the temporal trends of community structure
  and the one of community biomass. Lines correspond to the predictions of the
  linear models while the points are colored according the median community
  biomass of the three first years of the given temporal series. The lines
  surrounding each point represent the standard error associated to the temporal
  trends. Right panel displays the
  spatial relationship between median community structure over time and the
  median community biomass over time."
)

fig_rich_cap <- paste0(
  "Relationship between community structure and species richness. Left panel
  displays the relationships between the temporal trends of community structure
  and the one of species richness. Lines correspond to the predictions of the
  linear models while the points are colored according the median species
  richness of the three first years of the given temporal series. The lines
  surrounding each point represent the standard error associated to the temporal
  trends. Right panel displays the spatial relationship between median community
  structure over time and the median species richness over time."

)
```



```{r}
fig_bm_rich_cap <- paste0(
  "Relationships between the temporal trends of food-web structure
  and the ones of community biomass (left panel, A, C, E) species richness (right panel, B, D, F).
  The lines surrounding each point display the standard errors associated to
  the estimated temporal trends. Red and black lines represent respectively
  significant and non-significant slopes, both lines displays prediction from
  the Ordinary Least Squares model. The histograms display the distribution of response and predictive
  variables. Labels display the unstandardised slope coefficients and their
  standard errors (see Fig. \\ref{fig:std} for the standardized coefficients).
  $R^2$ are displayed only on the right panel, as it is the same model for both
  panels.")

```

```{r}
fig2 <- fig1_2
fig2$rich$log_bm_std <- NULL
fig2$rich <- map(fig2$rich,
  ~.x +
    theme(
      axis.text = element_text(size = 6),
      axis.title = element_text(size = 8)
      )
  )
fig2$bm <- map2(fig2$bm, names(fig2$rich),
  ~ .x + theme(
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8)
    ) +
  labs(
    y = paste0(var_replacement()[.y],
      "\ntrends (per year)"),
    x = lab_log_bm
  ) +
  scale_xy_log_trends(breaks = c(-.40, -.20, 0, .20, .40), axis = "x")
)
# Delete redondant legend
fig2$bm[[1]] <- fig2$bm[[1]] + theme(
  axis.text.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.title.x = element_blank()
  ) 
  

fig2$rich <- map(fig2$rich,
  ~ .x + theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank()
  ) +
  labs(x = lab_log_rich) +
  scale_xy_log_trends(breaks = c(-.10, -.050, 0, .050, .10), axis = "x")
  )
fig2$rich[[1]] <- fig2$rich[[1]] + theme(
  axis.text.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.title.x = element_blank()
  ) 
  

```

```{r}
# Add beta and Rsq
for (i in seq_along(fig2$rich)) {

  resp_var <- names(fig2$rich)[i]

  coeff_rich <- c(
    rsq = rsq_table_bm_rich_mono_stable_trends %>%
      filter(Response == resp_var) %$%
      unlist(.[, c("R.squared")]),
    reg_table_bm_rich_mono_stable_trends %>%
      filter(response == resp_var, term == "log_rich_std") %$%
      unlist(.[, c("estimate", "std.error", "std_estimate", "stdse")])
    ) %>%
  round(., 2)

  coeff_bm <- reg_table_bm_rich_mono_stable_trends %>%
    filter(response == resp_var, term == "log_bm_std") %$%
    unlist(.[, c("estimate", "std.error", "std_estimate", "stdse")]) %>%
    round(., 2)

  # Add coeff:
  fig2$rich[[resp_var]] <- fig2$rich[[resp_var]] +
  annotate("text", x = -.10, y = Inf, vjust = 1, hjust = 0,
    size = 2,
    parse = T,
    label = beta_rsq(
      rsq = coeff_rich["rsq"],
      beta = coeff_rich["estimate"],
      se = coeff_rich["std.error"]
    )
  )
  fig2$bm[[resp_var]] <- fig2$bm[[resp_var]] +
  annotate("text", x = -.4, y = Inf, vjust = 1, hjust = 0,
    size = 2,
    parse = T,
    label = beta_rsq(
      rsq = NULL,
      beta = coeff_bm["estimate"],
      se = coeff_bm["std.error"]
    )
  )
}
```

```{r}
# Add histograms
p_bef2 <- p_bef +
  theme(
  axis.text.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.title.x = element_blank()
  ) 
p_bef_hist <- ggMarginal(p_bef2, type = "histogram")
#fig2$bm[[1]] <- ggMarginal(fig2$bm[[1]], type = "histogram", margins = "x")
fig2$rich[[1]] <- ggMarginal(fig2$rich[[1]], type = "histogram", margins = "y")
fig2$rich[[2]] <- ggMarginal(fig2$rich[[2]], type = "histogram", margins = "y")
```

```{r}
sem_cap <- "Structural equation models on the temporal trends of the food-web
structure. The path display the standardized slopes and their associated 95%
  confidence intervals."
```


```{r sem, fig.cap = sem_cap}
ti <- magick::image_read(here::here("figures", "sem_tps_avg_weight_ok.svg"),  density = 300)
ggdraw() +
  draw_image(ti,
    x = 0, y = 0, hjust = 0, vjust = 0, width = .9, height = 1)
```



```{r bmr, out.width="100%", fig.height=7, fig.cap=fig_bm_rich_cap}
p <- draw_image(here::here("figures", "sem_tps_avg_weight_ok.pdf"),
  x = 1, y = 1, hjust = 1, vjust = 1, width = 0.13, height = 0.2)
biplot_model <- plot_grid(
  plot_grid(, p_bef_hist,
    labels = c("", "A"), ncol = 2,
    rel_widths = c(.62, 1)
    ),
  plot_grid(
  plot_grid(plotlist = fig2$bm,
    ncol = 1, labels = c("B", "D"),
    hjust = -5.5, vjust = 1.75
    ),
  plot_grid(plotlist = fig2$rich,
    ncol = 1, labels = c("C", "E"),
    hjust = -2, vjust = 1.75
    ),
  ncol = 2,
  rel_widths = c(.85, 1)
  ),
  nrow = 2,
  rel_heights = c(.6, 1)
)
save_plot(
  filename = here::here("figures", "biplot_model.png"),
  biplot_model)


biplot_model
```


```{r}
std_cap <- paste0(
  "Assessment of the space-for-time hypothesis. Standardized coefficients
  ($r_\\delta$) derived from the spatial and temporal Structural Equation
  Models. The left, middle and right panels display respectively the direct,
  indirect and total effects of community biomass and species richness on the
  Average trophic level (top panel), the connectance (middle panel) and the
  community biomass (bottom panel) The lines display the confidence intervals at
  95%.")

```

```{r std-old, eval = FALSE, fig.cap=std_cap, fig.width=6}
#loadd(fig_std_coef)
std_table_bm_rich_mono_stable_trends %>%
  filter(
    term %in% c("log_rich_std", "log_bm_std"),
    !response %in% "piel_nind") %>%
  mutate_at(vars(term, response), ~str_replace_all(., var_replacement(
        several_lines = TRUE))) %>%
  mutate(
    type = str_to_sentence(type),
    type = factor(type, levels = c("Temporal", "Spatial"))) %>%
  ggplot(aes(y = std_estimate, x = response, fill = type)) +
  viridis::scale_fill_viridis(begin = 0.5, end = 1, discrete = TRUE) +
  facet_grid(rows = vars(term)) +
  geom_col(position = position_dodge(width = .9)) +
  geom_linerange(aes(ymin = std_estimate - stdse, ymax = std_estimate + stdse),
    position = position_dodge(width = .9)) +
  labs(
    x = "Response variables",
    y = expression(paste("Standardized slope coefficients ", r[delta])),
    fill = "Model") +
  theme(legend.position = c(0.6, .05),
    legend.direction = "horizontal",
    text = element_text(size = 8), axis.text = element_text(size = 8)) +
  scale_y_continuous(sec.axis = sec_axis(~ ., name = "Predictive variable",
      breaks = NULL, labels = NULL))
```

```{r std, fig.cap=std_cap, fig.width=6, fig.height = 9}
load(here::here("data", "semeff.rda"))
load(here::here("data", "sp_semeff.rda"))
sp_semeff_tab <- from_semEff_to_table(sp_semeff)
semeff_tab <- from_semEff_to_table(semeff)


semeff_tot <- rbind(
  tibble(semeff_tab, model = "temporal"),
  tibble(sp_semeff_tab, model = "spatial")
  ) %>%
filter(
  !predictor %in% c("log_RC1", "log_RC2"),
  effect_type != "mediators"
)

semeff_tot %>%
  mutate(
    response = var_replacement()[response],
    predictor = var_replacement()[predictor]
    ) %>%
  ggplot(aes(x = predictor, y = effect, color = model)) +
  geom_hline(yintercept = 0) +
  geom_pointrange(aes(ymin = lower_ci, ymax = upper_ci), position = position_dodge(width = 0.4)) +
  facet_grid(rows = vars(response), cols = vars(effect_type)) +
  labs(
    x = "Predictor",
    y = expression(paste("Standardized slope coefficients ", r[delta])),
    color = "Model") +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```


# Discussion

We found that most temporal trends of food-webs were classified as
stable for species richness and community biomass. Roughly the same
number of stations displayed temporal decrease and increase for species
richness, and twice more stations displayed decrease in community biomass than
increase. This result is in accordance with previous meta analysis on species
richness trends of vertebrate in marine, freshwater and terrestrial systems
[@dornelas_assemblage_2014; @blowes_geography_2019; @klink_meta-analysis_2020].

## Species richness and community biomass are positively linked in space and time

Spatially and temporally, species richness scaled positively with community
biomass. Spatially, this result is in accordance with previous studies in stream
communities [@woods_testing_2020; @danet_species_nodate] but also in grasslands,
salt marches and forests [@hector_plant_1999; @tilman_biodiversity_2014;
@wu_relationship_2015; @li_relationship_2018; but see @grace_integrative_2016].
Therefore, our results confirm that Biodiversity-Ecosystem functioning
prediction works also in the temporal dynamics of food-webs. The positive
relationship between species richness and total biomass might be due to positive
complementarity in resource use [@carey_determining_2011], which is held by
niche differentiation [@loreau_biodiversity_1998; @loreau_partitioning_2001] or
to the higher probability of getting high biomass species with higher species
richness [@loreau_biodiversity_2001].

## Food-web structure changes according to the temporal trends of community biomass and species richness 

While we found a strong relationship between the temporal trends of community
biomass and the one of species richness, our results suggest that temporal
trends in community biomass and species richness are associated with very
different temporal trends on the connectance, average trophic level and evenness
of biomass. Indeed, temporal trends of connectance and average trophic level
were positively associated to the temporal trends of community biomass while no
significant association was found with temporal trends of species richness.
Moreover, the temporal trends of biomass evenness were negatively associated to
the temporal trends of community biomass whereas positively associated to
temporal trends of species richness. All together, it suggests that temporal
trends of community biomass and species richness are related to different
assembly and disassembly processes in food-webs. 

The temporal trends of connectance were positively linked to that of community
biomass, meaning that when connectance increased through time when community
biomass increased through time in a given site. Reversely, connectance decreased
in food-webs when community biomass decreased through time.  Indeed, food-webs
have a highly nested structure, in a way that feeding trophic links of species
at lower trophic level are a subset of the ones of species found at higher
trophic level [@kondoh_food_2010; @nordstrom_nestedness_2015]. It is because
feeding interactions are largely driven by body size, consumers being larger
than their preys [@brose_allometric_2006; @woodward_body_2005]. We also found
that community biomass losses through time were associated to a temporal
decrease of average trophic level and that community biomass temporal gains were
associated to temporal increase of average trophic level. Together with connectance, it suggests that
community biomass losses and gains are associated to losses and gains in large
bodied piscivores, i.e. biomass at the higher trophic level. Another piece of evidence
is that evenness of biomass, measured by the Pielou index, decreased through
time as community biomass increased, meaning that biomass distribution across
species becomes less even when community biomass increased. Reversely, in
food-webs that displayed temporal decrease in community biomass, we found that
evenness of biomass increased, i.e. that biomass distribution across species
becomes more even. Because predator-prey interactions relate on bodysize for a
large part [@brose_allometric_2006; @woodward_body_2005] and thus bodymass to a
certain extent, we can expect that a given gain in predators of higher trophic
level leads to a decrease of biomass evenness and reversely. In the same line,
we found that the temporal trends of community biomass were positively
associated to the temporal trends of the number and proportion of piscivorous
trophic species present in fish communities (Fig. SXX). The close association
between the temporal trends of community biomass from one side, and connectance,
average trophic level and biomass evenness from the other side, strongly suggest
that temporal trends in community biomass in natural freshwater fish communities
are associated to variations in the biomass of the top trophic level.

In contrast, we found that temporal trends of connectance and average trophic
level were not related to the temporal trends of species richness, in
contradiction with previous observation in space [@dunne_network_2006;
@danet_species_nodate]. However, we found that temporal trends of the number of
piscivorous species and piscivorous trophic species were positively associated
to the temporal trends of species richness (Fig. S3). It suggests that the
temporal decrease of species richness observed in our data are concomitant to
losses of piscivorous and non-piscivorous species, leading to the absence of
temporal trends in connectance and average trophic level and symmetrically for
the temporal increase of species richness. Furthermore, we found that the
temporal trends of biomass evenness had a positive relationship with the one of
species richness, in contradiction of what we found for temporal trends of
community biomass. Together with the fact that species richness temporal trends
had a positive relationship with the temporal trends of community biomass, it
suggests that positive and negative  temporal trends of species richness are
linked to gains and losses of redundancy in food-webs, without overall effects
on connectance and average trophic level. This is in line with the insurance
hypothesis [@yachi_biodiversity_1999] which predicts the temporal loss and gain
of species richness represent respectively loss and gain of redundancy in the
community, in the food-web structure in the present study.


The discrepancy between the effects of the temporal trends of species richness
and community biomass on food-web structure might be coined in the concepts of
trophic complementarity and redundancy [@poisot_trophic_2013;
@nordstrom_nestedness_2015]. The variations of community
biomass is related to variations in the presence of large bodied predators,
which affect both trophic complementarity, because they feed on bigger preys,
and redundancy, because their diet include the diet of lower trophic level.
Species richness temporal variation seems to affect mainly trophic redundancy
and not trophic complementarity, as average trophic level and connectance does
not change despite concomitant variations in the number of piscivorous species
(**Interesting ?**).

As studies reported community biomass or species richness temporal trends
[@hallmann_more_2017; @ceballos_biological_2017; @dornelas_assemblage_2014;
@blowes_geography_2019], we document that temporal trends of species richness
and community biomass might have different consequences on the structure of the
community. In particular, the decrease of the average trophic level associated
to the loss of community biomass could have cascading effect on ecosystem
functioning as the highest predators are predicted to increase productivity and
stabilise communities [@wang_biodiversity_2018; @shanafelt_stability_2018;
@danet_species_nodate]. In contrasts, the loss of species richness might be
linked to loss of redundancy in the food-web, highlighting that those
communities may become more at risk regarding future perturbations
[@yachi_biodiversity_1999]. Interestingly, the hypothesis that temporal trends
in community biomass is related to higher trophic level in our system has a
strong reasoning with the effect of human fisheries in marine systems which
affect primarily fish species at top trophic level [@sprules_surfing_2016].
Overall, our study highlights that monitoring several facets of biodiversity is
essential to infer how ecological communities are reshaped by loss and gain of
biomass and species richness.


## Space-for-time substitution does not always hold

In time and space, we found that connectance was positively linked to community
biomass. This result is also in accordance with theoretical work showing that
higher food-web connectance can result in higher community biomass
[@thebault_food-web_2003], or lower [@poisot_trophic_2013], highlighting that
the relation between connectance and community biomass may be dependant on how
food-web structure change with community biomass. Likewise, we found that
average trophic level had a positive relationship with community biomass in
space and time, in accordance with a theoretical study predicting an increase of
community biomass subsequent to the presence of higher predators
[@wang_biodiversity_2018]. We also found that biomass evenness was negatively
related to community biomass in space and time. This result is in accordance
with the reported top-heavy shape of biomass pyramids in food-webs,
particularly in freshwater systems [@mccauley_prevalence_2018]. Many mechanisms
have been invoked to explain this pattern but omnivory, which
is present in most of piscivorous species in our dataset, may favor this shape
by increasing food transfer efficiency toward the higher trophic levels.

Surprisingly, we found that the temporal trends of connectance were not related
to the one of species richness as found spatially in most empirical food-webs
[@dunne_network_2006] and also here. We explained this pattern by the fact that
the temporal variation of species richness in our dataset seems to be linked to
temporal variation of redundancy level in the structure of food-webs rather than
overall change of their vertical structure. The same rational can applied with
average trophic level. This result is in line with other studies which found
mismatch between spatial and temporal patterns [@adler_contrasting_2007;
@johnson_testing_2008]. This discrepancy in space and time might be due to the
crucial assumption that variations in space reflect differences in assembly
stages of ecological communities and then mirrors their temporal
assembly/disassembly trajectories. Temporal variation of species richness might
relate on transitory dynamics while spatial gradient reflect aggregated dynamics
over longer time scale including a far number of processes including high
species turnover along spatial gradient. However, we fount that the positive
relationship between evenness of biomass and species richness were consistent in
space and time. Another reason might be that the spatial gradient displays a
higher range of variation for species richness than the temporal stations (Fig.
S2). However, we found strong relationships between the temporal trend of
species richness from one side and the temporal trends of community biomass,
biomass evenness, and the number of piscivorous species from the other side (Fig. S3).
  
---
### Biomass and richness gains and losses are symmetric processes in terms of community structure
#
#We found no case in which gain or losses of biomass and richness lead to
#different relationship between the temporal dynamic of community structure and
#the one of biomass and species richness. We could have imagined that
#extinction/colonisation processes or immigration/extinction debt could have lead
to different relationships.
---

## Conclusion and perspectives

Our study suggests that richness and biomass temporal trends in natural fish
communities relate on different ecological processes, biomass temporal dynamics
being related to variations of food-web structure at the higher trophic levels
while species richness impacts redundancy of species in food-web structure. Our
result also suggests that space for time substitution may be relevant to predict
the effects of community biomass losses or gains on food-web structure. However,
our findings suggest that space-for-time substitution might not work for species
richness. Our study calls for further investigations to support the generality of
assembly rules in food-webs. They are crucial to better understand the
assembly and disassembly of food-web and then predict its impact on ecosystem
functioning.

# References  {-}

<div id="refs"></div>

\newpage





